|

### 2021-01-13 01-Chp-Introduction.Rmd
End of day: -621
End of day: -3533
End of day

@@

## Theoretical framework
The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.

@@

### Papers under review

@@

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)'}
Hold
```
(ref:intro-quote) --- Hold

@@

## Theoretical framework
The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.

@@

### Papers under review/Preprints

@@

### Peer review

* 2 papers for Systematic Reviews
* 1 paper for Environment International
* 1 paper for Journal of Clinical Epidemiology

### 2021-01-13 04-Chp-Systematic-Review.Rmd
End of day

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliabilty was chosen over other methods of assessing inter-rater reliability such as percent agreeement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does. [@cohen1960: [@gwet2008; @wongpakaran2013]

@@

<!----------------------------------------------------------------------------->
``` {r gwet-setup, results="hide", message=FALSE}
```

```{r gwet-table, message=FALSE, results="asis"}
```
<!----------------------------------------------------------------------------->

@@

```{r agreementtableinter, echo = FALSE}
```

```{r agreementtableintra, echo = FALSE}
```

@@

[This is a test]{.correction}

@@

A key limitation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use. In addition, there was limited literature available - as discussed in CHapter \@ref()

>>>>

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliabilty was chosen over other methods of assessing inter-rater reliability such as percent agreeement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does. [@cohen1960: @gwet2008; @wongpakaran2013]

@@

<!----------------------------------------------------------------------------->
<!-- # ``` {r gwet-setup, results="hide", message=FALSE} -->
<!-- # ``` -->
<!-- # -->
<!-- # ```{r gwet-table, message=FALSE, results="asis"} -->
<!-- # ``` -->
<!----------------------------------------------------------------------------->

@@

<!-- # ```{r agreementtableinter, echo = FALSE} -->
<!-- # ``` -->
<!-- # ```{r agreementtableintra, echo = FALSE} -->
<!-- # ``` -->

@@

@@

A key limitation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use. In addition, there was limited literature available - as discussed in CHapter \@ref(sys-rev)
